Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman equation (a PDE which
characterizes the value function for continuous space-time). We refer to
\cite{cont_rl} and the references therein. In particular \TODO{cite
Munos, convergence of sol to HJB.}  \cite{cont_rl} focusses on practical
algorithms for the continuous space-time case, including advantage
updating.

Here on the other hand we focus on generic RL algorithms that can handle
both discrete and continuous time and space, without collapsing in
continuous time, thus being robust to changing the timestep.

>>>>

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman equation (a PDE which
characterizes the value function for continuous space-time). We refer to
\cite{cont_rl} and the references therein. In particular \TODO{cite
Munos, convergence of sol to HJB.}  The corresponding algorithms are
often impractical \cite{cont_rl} for larger-dimensional problems.
\cite{cont_rl} focusses on practical algorithms for the continuous
space-time case, including advantage updating.

Here on the other hand we focus on generic RL algorithms that can handle
both discrete and continuous time and space, without collapsing in
continuous time, thus being robust to arbitrary timesteps.
